---
title: "multiOmics integration"
output: html_notebook
---


```{r}
#BiocManager::install("microbiome")
```

```{r}
library(reshape2)
library(corrplot)
library(MASS)
library(car)
library(lattice)
library(microbiome)
library(pheatmap)
```

```{r}
pcb.level <- read.csv("PCB_levels_for_integration.csv", na = "0")
pcb.level$exposure<-factor(pcb.level$exposure)
pcb.level$Tissue<-factor(pcb.level$Tissue)
```

```{r}
plotcor = function(mydata, title){
  nn = nrow(mydata)
  x <- as.matrix(mydata[, -(1:42)]) 
  y <- as.matrix(mydata[, 4:42])
  cor.matrix = cor(x, y, method="spearman", use = "pairwise.complete.obs")
  write.csv(cor.matrix, file = paste(title, ".csv", sep=""))
}

```

```{r}
raw<-read.csv("Results_spreadsheets/Liv_counts_for_integration.csv")

df1<-raw[ 1]
df2<-raw[,2:23]
raw<-df2[df2$Genes %in% df1$DEGs,]
names(raw)<-NULL
```

```{r}
######################### Liver #########################
ids = read.csv("Results_spreadsheets/Liv_counts_for_integration.csv", header = FALSE, nrows = 1)
ids<- ids[3:23]
#raw = read.csv("Results_spreadsheets/Liv_counts_for_integration.csv", header = FALSE, skip = 1)
micro = as.data.frame(t(raw[,-1]))
names(micro) <- raw[,1]
micro$Animal_ID = t(ids)
mydata = merge(pcb.level, micro, by="Animal_ID")

#plotcor(subset(mydata, exposure == "veh"), title = "Liver Veh")
plotcor(subset(mydata, Tissue == "liver" & exposure == "0.1"), title = "Liver 0.1 mg_kg")
plotcor(subset(mydata, Tissue == "liver" &exposure == "1"), title = "Liver 1 mg_kg")
plotcor(subset(mydata,Tissue == "liver" &  exposure == "6"), title = "Liver 6 mg_kg")
```


###Plotting results
####Heatmap
Heatmaps are a good way to visualize the most significant genes
```{r}
L_A<- read.csv("Liver 0.1 mg_kg.csv")
L_A<-melt(L_A, na.rm = TRUE)

```

```{r}
tiff(file = "Liver_0.1_correlation_heatmap.tiff", units="in", width=8, height=5, res=1000)
heat<- heat(L_A, "X", "variable", 
            fill = "value" ,
            order.cols = TRUE,
            order.rows = TRUE
            )+
  ggtitle("Liver 0.1 mg/kg correlation")+
  theme(text=element_text(size=5), 
        axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.key.size = unit(0.3, "cm"))
heat 

dev.off()

heat

```

```{r}
L_A<- read.csv("Liver 1 mg_kg.csv")
L_A<-melt(L_A, na.rm = TRUE)

```
```{r}
tiff(file = "Liver_1_correlation_heatmap.tiff", units="in", width=8, height=5, res=1000)
heat<- heat(L_A, "X", "variable", 
            fill = "value" ,
            order.cols = TRUE,
            order.rows = TRUE
            )+
  ggtitle("Liver 1 mg/kg correlation")+
  theme(text=element_text(size=5), 
        axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.key.size = unit(0.3, "cm"))
heat 

dev.off()

heat

```
```{r}
L_A<- read.csv("Liver 6 mg_kg.csv")
L_A<-melt(L_A, na.rm = TRUE)

```
```{r}
tiff(file = "Liver_6_correlation_heatmap.tiff", units="in", width=8, height=5, res=1000)
heat<- heat(L_A, "X", "variable", 
            fill = "value" ,
            order.cols = TRUE,
            order.rows = TRUE
            )+
  ggtitle("Liver 6 mg/kg correlation")+
  theme(text=element_text(size=5), 
        axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.key.size = unit(0.3, "cm"))
heat 

dev.off()

heat

```

```{r}
######################### Prefrontal Cortex #########################
ids = read.csv("Results_spreadsheets/PFC_counts_for_integration.csv", header = FALSE, nrows = 1)
ids<- ids[3:23]
#raw = read.csv("Results_spreadsheets/Liv_counts_for_integration.csv", header = FALSE, skip = 1)
micro = as.data.frame(t(raw[,-1]))
names(micro) <- raw[,1]
micro$Animal_ID = t(ids)
mydata = merge(pcb.level, micro, by="Animal_ID")

#plotcor(subset(mydata, exposure == "veh"), title = "Liver Veh")
plotcor(subset(mydata, Tissue =="brain" & exposure == "0.1"), title = "PFC 0.1 mg_kg")
plotcor(subset(mydata,Tissue =="brain" &  exposure == "1"), title = "PFC 1 mg_kg")
plotcor(subset(mydata,Tissue =="brain" &  exposure == "6"), title = "PFC 6 mg_kg")
```


###Plotting results
####Heatmap
Heatmaps are a good way to visualize the most significant genes
```{r}
L_A<- read.csv("PFC 0.1 mg_kg.csv")
L_A<-melt(L_A, na.rm = TRUE)

```

```{r}
tiff(file = "PFC_0.1_correlation_heatmap.tiff", units="in", width=8, height=5, res=1000)
heat<- heat(L_A, "X", "variable", 
            fill = "value" ,
            order.cols = TRUE,
            order.rows = TRUE
            )+
  ggtitle("PFC 0.1 mg/kg correlation")+
  theme(text=element_text(size=5), 
        axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.key.size = unit(0.3, "cm"))
heat 

dev.off()

heat

```

Heatmaps are a good way to visualize the most significant genes
```{r}
L_A<- read.csv("PFC 1 mg_kg.csv")
L_A<-melt(L_A, na.rm = TRUE)

```

```{r}
tiff(file = "PFC_1_correlation_heatmap.tiff", units="in", width=8, height=5, res=1000)
heat<- heat(L_A, "X", "variable", 
            fill = "value" ,
            order.cols = TRUE,
            order.rows = TRUE
            )+
  ggtitle("PFC 1 mg/kg correlation")+
  theme(text=element_text(size=5), 
        axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.key.size = unit(0.3, "cm"))
heat 

dev.off()

heat

```

Heatmaps are a good way to visualize the most significant genes
```{r}
L_A<- read.csv("PFC 6 mg_kg.csv")
L_A<-melt(L_A, na.rm = TRUE)

```

```{r}
tiff(file = "PFC_6_correlation_heatmap.tiff", units="in", width=8, height=5, res=1000)
heat<- heat(L_A, "X", "variable", 
            fill = "value" ,
            order.cols = TRUE,
            order.rows = TRUE
            )+
  ggtitle("PFC 6 mg/kg correlation")+
  theme(text=element_text(size=5), 
        axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.key.size = unit(0.3, "cm"))
heat 

dev.off()

heat

```

```{r}
######################### Striatum #########################
ids = read.csv("Results_spreadsheets/STN_counts_for_integration.csv", header = FALSE, nrows = 1)
ids<- ids[3:23]
#raw = read.csv("Results_spreadsheets/Liv_counts_for_integration.csv", header = FALSE, skip = 1)
micro = as.data.frame(t(raw[,-1]))
names(micro) <- raw[,1]
micro$Animal_ID = t(ids)
mydata = merge(pcb.level, micro, by="Animal_ID")

#plotcor(subset(mydata, exposure == "veh"), title = "Liver Veh")
plotcor(subset(mydata, Tissue =="brain" & exposure == "0.1"), title = "STN 0.1 mg_kg")
plotcor(subset(mydata,Tissue =="brain" &  exposure == "1"), title = "STN 1 mg_kg")
plotcor(subset(mydata,Tissue =="brain" &  exposure == "6"), title = "STN 6 mg_kg")
```


###Plotting results
####Heatmap
Heatmaps are a good way to visualize the most significant genes
```{r}
L_A<- read.csv("STN 0.1 mg_kg.csv")
L_A<-melt(L_A, na.rm = TRUE)

```

```{r}
tiff(file = "STN_0.1_correlation_heatmap.tiff", units="in", width=8, height=5, res=1000)
heat<- heat(L_A, "X", "variable", 
            fill = "value" ,
            order.cols = TRUE,
            order.rows = TRUE
            )+
  ggtitle("STN 0.1 mg/kg correlation")+
  theme(text=element_text(size=5), 
        axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.key.size = unit(0.3, "cm"))
heat 

dev.off()

heat

```

Heatmaps are a good way to visualize the most significant genes
```{r}
L_A<- read.csv("STN 1 mg_kg.csv")
L_A<-melt(L_A, na.rm = TRUE)

```

```{r}
tiff(file = "STN_1_correlation_heatmap.tiff", units="in", width=8, height=5, res=1000)
heat<- heat(L_A, "X", "variable", 
            fill = "value" ,
            order.cols = TRUE,
            order.rows = TRUE
            )+
  ggtitle("STN 1 mg/kg correlation")+
  theme(text=element_text(size=5), 
        axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.key.size = unit(0.3, "cm"))
heat 

dev.off()

heat

```

Heatmaps are a good way to visualize the most significant genes
```{r}
L_A<- read.csv("STN 6 mg_kg.csv")
L_A<-melt(L_A, na.rm = TRUE)

```

```{r}
tiff(file = "STN_6_correlation_heatmap.tiff", units="in", width=8, height=5, res=1000)
heat<- heat(L_A, "X", "variable", 
            fill = "value" ,
            order.cols = TRUE,
            order.rows = TRUE
            )+
  ggtitle("STN 6 mg/kg correlation")+
  theme(text=element_text(size=5), 
        axis.text.x = element_text(angle = 45, hjust = 1), 
        legend.key.size = unit(0.3, "cm"))
heat 

dev.off()

heat

```